Adopting agile in the large: motivations, success factors and challenges

### 2014-05-04 journal/article.tex
By the book is not good

@@

@@

>>>>

% Misconceptions of agile

@@

Even if there was no misunderstandings the correct agile model was found hard to
implement. Several cases describe how an agile model was hard to learn from
literature [P21, P27], especially when it comes to implementing it on a large
scale [P13]. As Beavers [P5] writes: ``There simply was not a manual or document
where we could find easy answers on how to do things''.
Schnitter and Mackert [P45] report that theoretical considerations on how to
scale up the agile methos were not good enough, and that product managers and
architects struggled when several Scrum teams were working concurrently.
Another case concluded that all practices prescribd in XP did not fit enterprise
scale development, and some practices required customization [P49]. It would not
be good to prescribe practices with a check list as it would impose a single
model in an organization with several individual teams and projects [P41].

Further indications were given that the advice given in literature will not
ferry all the way. Benefield [P6] describes how it was dificult finding a
balance between prescribing a by-the-book implementation which may put people
off, and giving too much freedom in the agile methods which may weaken core
practices.
The reality where the practices needed to be applied was described as
messy in comparison to the ideal circumstances presented in literature, which
made it difficult to choose an initial model and gain buy-in for it [P10].
Difficulties in choosing the model to start with were also due to variances
perceived in the agile approaches suggested in literature [P30].

@@

\subsubsection{Large organization issues}
